\subsection{Airline Statistics}

\subsubsection*{a) Shortest Flight Distance}
The minimal distance for airline ID 20436 is 332.

\lstinputlisting[language={},numbers=left,numberstyle=\tiny,frame=single,breaklines=true,postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}]{../src/5_hadoop/1a_shortest_flight_distance/out/part-00000.}
\lstinputlisting[language={},numbers=left,numberstyle=\tiny,frame=single,breaklines=true,postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}]{../src/5_hadoop/1a_shortest_flight_distance/hrun.out}



\subsubsection*{b) Late Arrival Counts}
The percentage of flight delays for airline ID 20436 is 0.295.
\lstinputlisting[language={},numbers=left,numberstyle=\tiny,frame=single,breaklines=true,postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}]{../src/5_hadoop/1b_late_arrival_counts/out/part-00000.}
\lstinputlisting[language={},numbers=left,numberstyle=\tiny,frame=single,breaklines=true,postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}]{../src/5_hadoop/1b_late_arrival_counts/hrun.out}


\subsubsection*{c) Mean and Standard deviation for Arrival Delay}
The mean and standard deviation for airline ID 20436 are 1.717 and 46.18.
The mean and Standard deviation have been computed using Wilbur's method : the mapper streams the data, the combiner uses a streaming version of the algorithm, while the reducers use the parallel execution version of the algorithm.
\lstinputlisting[language={},numbers=left,numberstyle=\tiny,frame=single,breaklines=true,postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}]{../src/5_hadoop/1c_mean_std_arrival_delay/out/part-00000.}
\lstinputlisting[language={},numbers=left,numberstyle=\tiny,frame=single,breaklines=true,postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}]{../src/5_hadoop/1c_mean_std_arrival_delay/hrun.out}

\subsubsection*{d) Top-10 Arrival Delays}
The 10 most delayed flights for airline ID 20436 are 1285, 1298, 291, 1124, 720, 1135, 249, 1248, 733, 756.
The mappers extract the relevant data, the combiners aggregate it into dictionaries and send it to the reducers.
\lstinputlisting[language={},numbers=left,numberstyle=\tiny,frame=single,breaklines=true,postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}]{../src/5_hadoop/1d_top10_arrival_delays/out/part-00000.}
\lstinputlisting[language={},numbers=left,numberstyle=\tiny,frame=single,breaklines=true,postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}]{../src/5_hadoop/1d_top10_arrival_delays/hrun.out}


\subsection{Landsat Statistics}
The mapper fills up chunks of the data into a larger numpy array. Once the array is filled, they are used to generate predictions all at the same time, therefore speeding up computation considerably.

\lstinputlisting[language={},numbers=left,numberstyle=\tiny,frame=single,breaklines=true,postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}]{../src/5_hadoop/2_landsat_stats/out/part-00000.}

\lstinputlisting[language={},numbers=left,numberstyle=\tiny,frame=single,breaklines=true,postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}]{../src/5_hadoop/2_landsat_stats/hrun.out}
